---
title: "Iteration_ii"
author: "Rachel"
date: "11/14/2021"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(rvest)

knitr::opts_chunk$set(
  fig.width = 6, 
  fig.asp = .6, 
  out.width = "90%"
)

theme_set(theme_minimal()+theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
```

## Lists

you can put anything in a list. 

```{r}
l = list(
  vec_numeric = 5:8,
  vec_logical = c(TRUE, TRUE, FALSE, TRUE, FALSE, FALSE),
  mat = matrix(1:8, nrow = 2, ncol = 4),
  summary = summary(rnorm(100))
) 
```

```{r, error = FALSE}
l
l$vec_numeric
l[[1]]
mean(l[["vec_numeric"]])
```

## 'for' loop

create a new list

```{r}
list_norm = 
  list(
    a = rnorm(20, mean = 3, sd = 1),
    b = rnorm(20, mean = 0, sd = 5),
    c = rnorm(20, mean = 10, sd = 2),
    d = rnorm(20, mean = 3, sd = 1)
    
  )
```


```{r}
list_norm
```
Pause and get my old function. 

```{r}
```{r, error = TRUE}
z_scores(3)
z_scores("my name is jeff")
z_scores(mtcars)
z_scores(c(TRUE, TRUE, FALSE, FALSE))
```

## Multiple outputs 

```{r}
mean_and_sd = function(x) {
  
  if (!is.numeric(x)) {
    stop("Input must be numeric")
  }
  
  if (length(x) < 3) {
    stop("Input must have at least three number")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)
  
  tibble(
    mean = mean_x,
    sd = sd_x
  )

  
}
```

I can apply that function to each list element. 

```{r}
mean_and_sd(list_norm[[1]])
mean_and_sd(list_norm[[2]])
mean_and_sd(list_norm[[3]])
mean_and_sd(list_norm[[4]])
```

Let's use a for loop: 

```{r}
output = vector("list", length = 4)

for (i in 1:4) {
  output[[i]] = mean_and_sd(list_norm[[i]])
}
```

## Let's try map!

```{r}
output = map(list_norm, mean_and_sd)
```

waht if you want a different function...? 

```{r}
output = map(list_norm, median)
```

