---
title: "Iteration_ii"
author: "Rachel"
date: "11/14/2021"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(rvest)

knitr::opts_chunk$set(
  fig.width = 6, 
  fig.asp = .6, 
  out.width = "90%"
)

theme_set(theme_minimal()+theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
```

## Lists

you can put anything in a list. 

```{r}
l = list(
  vec_numeric = 5:8,
  vec_logical = c(TRUE, TRUE, FALSE, TRUE, FALSE, FALSE),
  mat = matrix(1:8, nrow = 2, ncol = 4),
  summary = summary(rnorm(100))
) 
```

```{r, error = FALSE}
l
l$vec_numeric
l[[1]]
mean(l[["vec_numeric"]])
```

## 'for' loop

create a new list

```{r}
list_norm = 
  list(
    a = rnorm(20, mean = 3, sd = 1),
    b = rnorm(20, mean = 0, sd = 5),
    c = rnorm(20, mean = 10, sd = 2),
    d = rnorm(20, mean = 3, sd = 1)
    
  )
```


```{r}
list_norm
```
Pause and get my old function. 

```{r}
```{r, error = TRUE}
z_scores(3)
z_scores("my name is jeff")
z_scores(mtcars)
z_scores(c(TRUE, TRUE, FALSE, FALSE))
```

## Multiple outputs 

```{r}
mean_and_sd = function(x) {
  
  if (!is.numeric(x)) {
    stop("Input must be numeric")
  }
  
  if (length(x) < 3) {
    stop("Input must have at least three number")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)
  
  tibble(
    mean = mean_x,
    sd = sd_x
  )

  
}
```

I can apply that function to each list element. 

```{r}
mean_and_sd(list_norm[[1]])
mean_and_sd(list_norm[[2]])
mean_and_sd(list_norm[[3]])
mean_and_sd(list_norm[[4]])
```

Let's use a for loop: 

```{r}
output = vector("list", length = 4)

for (i in 1:4) {
  output[[i]] = mean_and_sd(list_norm[[i]])
}
```

## Let's try map!

```{r}
output = map(list_norm, mean_and_sd)
```

waht if you want a different function...? 

```{r}
output = map(list_norm, median)
```
```{r}
output = map(list_norm, median, .id = "input")
```
```{r}
output = map_df(list_norm, mean_and_sd, .id = "input")
```

## list columns!

```{r}
listcol_df = 
  tibble(
    name = c("a", "b", "c", "d"), 
    samp = list_norm
  )
```


```{r}
listcol_df %>% pull(name)
listcol_df %>% pull(samp)

listcol_df %>% 
  filter(name == "a")
```

Let's try some operations 

```{r}
mean_and_sd(listcol_df$samp[[1]])
mean_and_sd(listcol_df$samp[[2]])
```
Can I just map? 
```{r}
map(listcol_df$samp, mean_and_sd)

```
So.. can I add a list column?? 

```{r}
listcol_df = 
listcol_df %>% 
  mutate(summary = map(samp, mean_and_sd),
         medain = map_dbl(samp, median))
```
## Weather data

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USC00519397", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(
      id, 
      USW00094728 = "CentralPark_NY", 
      USC00519397 = "Waikiki_HA",
      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())

```
Get our list columns...

```{r}
weather_nest = 
  weather_df %>% 
  nest(data = date:tmin)
```

```{r}
weather_nest %>% pull(name)
weather_nest %>% pull(data)
```

Suppose I want to regress `tmax` on `tmin` for each station. 


```{r}
lm(tmax ~ tmin, data = weather_nest$data[[1]])
```
Let's write a function

```{r}
weather_lm = function(df) {
  lm(tmax ~ tmin, data = df)
}
output = vector("list", 3)
for(i in 1:3) {
  output[[i]] = weather_lm(weather_nest$data[[i]])
  
}
weather_lm(weather_nest$data[[1]])
weather_lm(weather_nest$data[[2]])
```
what about a map...?!

```{r}
weather_nest$data
```

what about a map in a list column!
```{r}
weather_nest %>%
  mutate(models = map(data, weather_lm))

weather_nest$models
```

